Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-02 analysis/paper/paper.Rmd
Rethink title to reflect the aims of our analysis
Edit section on good examples
Include comment on the non-open nature of the RICEPEST Python scripts and correct duplicated mention of Carlson and Grünwald

---
title: "Reproducibility in plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl"
---

@@

At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
A final example is provided by @carleson2019population who hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).

The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks et al. [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight. Similarly, @carleson2019population provided all data on OSF.io [@Carleson_Grünwald_2019].

>>>>

---
title: "Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson M. Del Ponte:
      institute: UFV
  - Kaique S. Alves:
      institute: UFV
  - Zachary S. L. Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97330, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/phytopath_template.docx"
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl"
---

@@

At the second level, -@Lehner2017 used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean yield (<https://emdelponte.github.io/paper-white-mold-meta-analysis/>).
The website clearly demonstrates the analysis to readers and uses R so that anyone can easily replicate the work.
Likewise, @Duku2016 provide scripts for models, data and code for graphs, via a website hosted by GitHub, <http://adamhsparks.github.io/MICCORDEA/>, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.
However, even this example is not totally open as it requires ArcGIS, an expensive proprietary software, to run the provided Python scripts for the RICEPEST model [@Savary2014].
This highlights the difficulty in making work completely open and reproducible, further work could be undertaken to make the Python scripts rely totally on free-open-source-software but the work as it it provided here does allow for the complete reproducibility of the paper as written provided with the proper tools.

The third level is the use of proper data repositories such as GitHub, FigShare, Zenodo or OSF.io among others, allow for the deposition and updating of code, figures, data preprints or any other materials that support the article itself while providing a DOI and citation for a standalone citation.
Sparks et al. [-@Sparks2011; -@Sparks2014] used FigShare to provide models, data and code, [@Sparks2016] necessary to replicate model development and the subsequent study on the effects of climate change on potato late blight.
Similarly, @carleson2019population hosted the code for reproducing a population genomic analysis of *Phytophthora plurivora* on GitHub, while providing all data on OSF.io (the Open Science Framework).
